\section*{Introduction}
The task was to implement an Finit State Machine in Simulink.
Afterwards this Finit State Machine is to be tested for its requirements.
Finally code should be generated and loaded onto the Arduino board. 

\section{Requirements}

	\subsection{Order of Priorities}
		
		\begin{enumerate}
			\item \textbf{Unlocking}\\
				This is the core of the task and so the most important requirement.
			\item \textbf{Locking}\\
				It is necessary to return to the locked state.
			\item \textbf{Sampling}\\
				With a sampletime of 10ms you do not have to debounce the inputs. In this case is sampling important.							
			\item \textbf{Wrong Sequence}\\
				This requirement makes it difficult to crack the code using the brute force method.
			\item \textbf{Input Handling}\\
				This is a nice feature and can be useful if you have mistyped.
			\item \textbf{State}\\
				It would be a nice feature to see the current state. But it is not essential.		
			\item \textbf{Keypad}\\
				It is absolutely irrelevant whether the numbers are compared as integers between 0-9 or as ACII integers between 48 - 57.
%			\item Voltage Monitoring
		\end{enumerate}	
The Voltage Monitoring is an own requirement. Because it has no connection with the remaining requirements.
	
	
	\subsection{Funcional and non functional requirements}
	Functional	\todo{Sort}
		\begin{itemize}
			\item Unlockin
			\item Wrong Sequence
			\item Input Handling
			\item State
			\item Sampling
			\item Locking
			\item Keypad
			\item Voltage Monitoring
		\end{itemize}
	Non functional
		\begin{itemize}
			\item sdgs
		\end{itemize}

	\subsection{Missing requirements}
	
		\begin{itemize}
			\item[Change Sequence] It would be useful if you could change the sequence while the program is running and not just when the program is freshly loaded onto the arduino board.
			\item[label] description
		\end{itemize}


\section{Stateflow implementation}
The two seperate requirements where implemented separately.

	\subsection{Numeric Sequence Lock}
	
	
	\subsection{Voltage Monitoring}


\section{Testing}


\section{Linkage/ Traceabity of requirements}


	\subsection{Links between Models and Requirements}
	
	
	\subsection{Create a Link from a Model Object to a Microsoft Word Requirements Document}
	
	
	\subsection{Requirements visibility and navigation}
	
	
	\subsection{Linkage of requirements to Signal Builder Block (Test Cases)}
	
	
	
	\subsection{Traceability/Report}
	
	
	\subsection{Automatic Test Case Generation for increasing coverage}
	
	
	
\section{Conclusion}